Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-02-04 PaperVictor.tex
Revise Victor's version

% !TeX spellcheck = en_US
\documentclass{article}
\usepackage{amsmath}
\usepackage{braket}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\newif{\ifmover}
\newif{\ifquitar}
\usepackage{authblk}
\renewcommand{\Affilfont}{\small}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaV}[1]{{\bf \em \color{green}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

@@

\begin{abstract}
Porous silicon is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. In the present work, we design
mirrors using \textit{chirped}-type structures and by stacking
appropriately tuned sub-mirrors, and we optimize the design parameters
to maximize the
optical reflectance $\braket{R}$ averaged within a wide
spectral range  covering the visible and near infrared regions, and
within a wide angular range. The chirped structures are found to be
more suitable for the visible range,
while stacked sub-mirrors are found to be better for the NIR
region. We design, fabricate and characterize
some of the optimized omnidirectional structures with less
than 100 pairs of layers. We obtained a structure that has the an
omnidirectional spectral width larger than those previously
reported.
\end{abstract}
\notaL{No sé si Vivechna quiera añadir al ICF y mencionar su estancia
  en los agrads.}
\section{Introduction}

Photonic crystal (PC)-based structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. In analogy to electrons in a
crystal, their propagation is forbidden if their energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
within in a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with an absolute band gap for all angles of incidence.
The use of metallic
mirrors is limited due to their relatively large absorption at the
visible (Vis) and near infrared (NIR) frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses corresponds to a quarter of a wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at their edges, resulting in a wider high-reflection band \cite{Xifre2009}.

On the other hand, different fabrication techniques have been used to
obtain omnidirectional (OD) mirrors that operate on the visible and/or
near infrared (Vis-NIR) range of the electromagnetic spectrum. For
example, Chen et al. \cite{Chen1999},
reported the fabrication of a structure made of six pairs of
 TiO$_{2}$/SiO$_{2}$  layers with
an OD band of about 70 nm in the NIR range, employing a sol-gel deposition
method. Park et al. \cite{Park2003}, used molecular beam epitaxy to
grow a stack of four pairs of GaAs/AlAs layers, followed by its conversion to
GaAs/Al$_{2}$O$_{3}$ by selective oxidation of the AlAs
layers, to obtain an OD with a band from 710 to 950 nm.
On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain a 150 nm wide omnidirectional band centered at
1750 nm. Furthermore, Jena et al. \cite{Jena2019},
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequen cy magnetron sputtering (for SiO$_{2}$
layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved an OD band from
592 to 668 nm. However, these techniques are expensive and they
require sophisticated equipment and long fabrication times. Use of PS
is an attractive alternative, since it can be easily manufactured by
electrochemical etching crystalline Si in an hydrofluoric
acid based electrolyte to obtain a sponge-like nanostructure composed
of Si and air. By modulating the supplied current and its application
time during the electrochemical reaction, it is possible to obtain
multilayered structures allowing for the fabrication OD mirrors \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of PS PC's, they have also been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
for photoluminescence control \cite{Antunez2014}. Recently, the study of
chirped multilayer structures has
increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
PS based dielectric optical filters, quasi-OD and OD mirrors have been extensively studied in different
regions of the electromagnetic spectrum, such as the ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003} region.
However, to obtain the desirable high index of refraction
contrast, layers of high porosity have to be employed, which makes the
resulting structures relatively fragile. In addition, use of high
porosity makes the fabrication of large structures, with a
very large number of layers, unfeasible. For this reason, in this work
we study different strategies to produce multilayered mirrors
with high reflectance omnidirectional band
with relatively small thickness and refractive index contrast.

@@

For the analysis of the propagation of electromagnetic fields through
multilayered systems it is usual to employ the transfer matrix
method \cite{PerezA2004,Pochi2005}. Assuming the system is 1D, with variations
only along the $z$ directions, and that the polarization of light is either
transverse electric (TE) or transverse magnetic (TM), the
transfer matrix $M\left(z_{2},z_{1}\right)$ is
a 2x2 matrix that relates the components of the electric $E_{\| }$
and magnetic  $H_{\|}$ fields parallel to the $xy$ plane
evaluated at $z_2$ to their value at $z_{1}$,
\begin{equation*}
	\left(
	\begin{array}{c}
		E_{\|} \\
		H_{\| }%
	\end{array}%
	\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
	\begin{array}{c}
		E_{\| } \\
		H_{\| }%
	\end{array}%
	\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain and use $M$
\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
for the numerically stable calculation of the reflectance of large
multilayer systems, as
proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the
supplementary information. The
explicit expressions for the optical coefficients are:
\begin{equation}
	r=\sigma \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
		M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
	t=\frac{2\zeta}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $M_{ij}$ are the elements
of the transfer matrix which transfer
the fields from its surface interface with vacuum at $z_0$ towards the
substrate at $z_s$,  $Z_0$ is the surface impedance of vacuum and $Z_s$ is the
surface impedance of the substrate, and we define $r=F_r/F_i$ and $t=F_t/F_i$ in terms
of the reflected and transmitted fields, where we choose the $F$'s as electric
fields for (TE) polarization and magnetic fields
for transverse magnetic polarization (TM). Here, $\sigma=-1$ and
$\zeta= Z_s$ for TE polarization, while
$\sigma=1$ and $\zeta=Z_0$ for TM
polarization.
The reflectance is given by
$R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for
TM polarization. The complex refractive index of the porous
layers were obtained through the Bruggeman's effective medium theory, which
has been reported to adequately reproduce the PS optical parameters
\cite{Giusseppe2011,Pap2006,Estrada2018}.

@@

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, $p$-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
\cite{Canham1990,Escorcia2007}. The electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous
hydrofluoric acid (HF) (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
However, as it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte
diffusivity problems \cite{Ariza2011}, the current
densities were chosen as 35 and 305 $\text{mA}/\text{cm}^{2}$,
with corresponding porosities of 51\% and 76\%, respectively.
These porosities were obtained through previously obtained calibration
curves using a gravimetric technique \cite{Pap2006}. The
etching rate of PS was obtained by synthetizing single layers under
similar conditions and measuring their thicknesses through Scanning
Electron Microscopy (SEM). Absolute reflectivity measurements were
carried out with a Perkin Elmer Lambda 950 UV/Visible
spectrophotometer with a variable angle universal reflectance
accessory (URA) for different incident angles $\theta _{i}=10^{\circ
}$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $50^{\circ }$ and
$60^{\circ }$ using non-polarized light. The maximum and minimum
values of $\theta _{i}$ were constrained by the angular range of the
equipment accessory URA.

@@

Here we study multilayered structures where the thicknesses for each
pair $j=0\ldots N_p-1$ of layers are tuned to a wavelength $\lambda_j$ which changes
gradually with the depth of the layer, according to
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j-1}{N_p-1}\right),\label{Dis}
\end{equation}%
where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
maximum {\em design} wavelengths respectively, $N_p$ is the number of
periods  in the structure and $f(\xi)$ is a smooth function that
goes from 0 to 1 as its argument goes from the surface ($\xi=0$) to the
substrate ($\xi=1)$. We only consider increasing functions $f$ due to
the high absorption of PS in the ultraviolet region, which decreases in
the visible and becomes negligible in the near infrared, so, that the first
periods are tuned in the UV-Vis regions. We consider the
following classes of functions:
\begin{equation}
f_{1}\left(\xi \right) =\xi^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
f_{2}\left(\xi \right) =\frac{1}{2}\left(\xi^{\alpha }+\xi^{\beta}\right)
\label{F2}
\end{equation}
and%
\begin{equation}
f_{3}\left(\xi\right) =A\xi^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize in order
to maximize the average reflectance $\braket{R}$ over given spectral
and angular ranges. The class
$f_{1}$ (Eq. (\ref {F1})) with  $\alpha>0$ corresponds to simple
increasing profiles, $f_2$ is the arithmetic mean
of two functions of the type $f_{1}$ with different
powers $\alpha$ and $\beta$, and $f_{3}$ (Eq. (\ref{F3})) is
designed so that the first term dominates near the surface and the
second near the substrate, to allow different behaviors
at the edges of the spectrum.
The parameters
$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize the
reflectance for non-polarized light $\braket{R}$ averaged in the
angular range of $0^\circ$ to $90^\circ$ and either in the
spectral region $\mathcal R_1$ from 350 to
1400 nm or $\mathcal R_2$ from 400 to 3000 nm. For $\mathcal R_1$ we took
$\lambda_{\min}$ as another parameter to be optimized while $\lambda_{\max}$
was fixed at 1400 nm. For $\mathcal R_2$ we fixed both
$\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm.
\notaL{Any reason
	for these choices? They seem arbitrary.} \notaL{Creo que alguna
	explicación  sencilla merece el lector.}
\notaV{Agregue:  }
Approximately $90\%$ of the solar radiation that reaches the
earth's surface is contained in the spectral region
$\mathcal R_1$, and $98\%$ in $\mathcal R_2$ \notaL{¿qué es
  terrestrial solar? terrestrial solar radiation} \cite{Bird1983}. A direct
application of the optimized structures in these regions is solar
reflectors. \notaL{¿Pero por qué en un caso dejasta $\lambda_{\min}$
  fijo y en el otro caso no? Sería bueno que el lector entienda todas
  las decisiones que sean fáciles de explicar}
The
optimized parameters corresponding to the low and high porosities $p_l=0.51$ and $p_h=0.76$
are shown in Table \ref{tab:tableA}.

\begin{table}
  \centering
  \label{tab:tableA}
  \addtolength{\tabcolsep}{-2pt}
    \begin{tabular}{rrrrrrrrrr}
      Class&$\alpha$&$\beta$&A&$\lambda_{min}(nm)$&$N_{p}$&$d(\mu\text{m})$       &ODW(nm)&ODC (nm)&$\braket{R}(\%)$\\
      \hline
      \hline
      $f_{1}$     &0.24    &---      &---     &250&222   &86.1    &300    &1150    &89\\
      $f_{2}$     &0.37    &1.06     &---     &400&102   &35.9    &220    &1110    &88\\
      $\bm{f_{3}}$&\bf 1.23&\bf 0.540&\bf 0.18&\bf 320&\bf 63&\bf 21.6&\bf 250&\bf 1125&\bf 89\\
      \hline
      $\bm{f_{1}}$&\bf 1.20&\bf ---  &\bf --- &\bf ---&\bf 90&\bf 60.4&\bf 2150&\bf 1925&\bf 92\\
      $f_{2}$     &1.08    &1.86     &---  &---  &105   &61.7    &2000    &2000    &89\\
      $f_{3}$     &1.01    &1.95     &0.20  &---  &102   &62.3    &2050    &1975    &90\\
    \end{tabular}
  \caption{Optimized parameters $\alpha$, $\beta$, $A$ and $N_p$ yielding the highest
    reflectance $\braket{R}$ averaged over the spectral ranges
    $\mathcal R_1$ (first block) and $\mathcal R_2$ (second block) and
    the angular range $0-90^\circ$ for the profile classes $f_1$, $f_2$ and
    $f_3$ (Eqs. (\ref{F1}) - (\ref{F3})). We include the thickness $d$
    of the structure and the omnidirectional spectral
    width and center (ODW and ODC).}
\end{table}
\notaL{¿Sería
	correcto citar a Xu, Ahmed y Reiner entonces, para apuntalar
	nuestra definición?}
\notaV{Agregue:   }
Various works use $R>90\%$ as a criterium for defining
omnidirectional band, and

>>>>

% !TeX spellcheck = en_US
\documentclass{article}
\usepackage{amsmath}
\usepackage{braket}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
%\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\newif{\ifmover}
\newif{\ifquitar}
\usepackage{authblk}
\renewcommand{\Affilfont}{\small}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaV}[1]{{\bf \em \color{green}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

@@

\begin{abstract}
Porous silicon is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. In the present work, we design
mirrors using \textit{chirped}-type structures and by stacking
appropriately tuned sub-mirrors, and we optimize the design parameters
to maximize the
optical reflectance $\braket{R}$ averaged within a wide
spectral range  covering the visible and near infrared regions, and
within a wide angular range. The chirped structures are found to be
more suitable for the visible range,
while stacked sub-mirrors are found to be better for the NIR
region. We design, fabricate and characterize
some of the optimized omnidirectional mirrors with less
than 100 pairs of layers. We obtained structures with a wider
omnidirectional spectral region than those previously
reported.
\end{abstract}
\notaL{No sé si Vivechna quiera añadir al ICF y mencionar su estancia
  en los agrads.}
\section{Introduction}

Photonic crystal (PC)-based structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
their energies are consequently organized into photonic bands. In
analogy to electronic bands withiny a
crystal, propagation is forbidden if the energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
within in a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with an absolute band gap for all angles of incidence.
The use of metallic
mirrors is limited due to their relatively large absorption at the
visible (Vis) and near infrared (NIR) frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses corresponds to a quarter of a wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at their edges, resulting in a wider high-reflection band \cite{Xifre2009}.

On the other hand, different fabrication techniques have been used to
obtain omnidirectional mirrors (ODM) that operate on the visible and/or
near infrared (Vis-NIR) range of the electromagnetic spectrum. For
example, Chen et al. \cite{Chen1999},
reported the fabrication of a structure made of six pairs of
 TiO$_{2}$/SiO$_{2}$  layers with
an omnidirectional band (ODB) of about 70 nm in the NIR range, employing a sol-gel deposition
method. Park et al. \cite{Park2003}, used molecular beam epitaxy to
grow a stack of four pairs of GaAs/AlAs layers, followed by its conversion to
GaAs/Al$_{2}$O$_{3}$ by selective oxidation of the AlAs
layers, to obtain an ODB from 710 to 950 nm.
On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide deposited by thermal evaporation and spin-casting
respectively, to obtain a 150 nm wide omnidirectional band centered at
1750 nm. Furthermore, Jena et al. \cite{Jena2019},
used sequential asymmetric bipolar pulsed DC magnetron sputtering for TiO$%
_{2}$ layers and radio frequency magnetron sputtering for SiO$_{2}$
layers to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved an ODB from
592 to 668 nm. However, these techniques are expensive and they
require sophisticated equipment and long fabrication times. Use of
porous silicon (PS)
is an attractive alternative, since it can be easily manufactured by
electrochemical etching crystalline Si in an hydrofluoric
acid based electrolyte to obtain a sponge-like nanostructure composed
of Si and air. By modulating the supplied current and its application
time during the electrochemical reaction, it is possible to obtain
multilayered structures allowing for the fabrication ODM's \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of PS PC's, they have also been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
for photoluminescence control \cite{Antunez2014}. Recently, the study of
chirped multilayer structures has
increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
PS based dielectric optical filters, quasi-ODM's and ODM's have been extensively studied in different
regions of the electromagnetic spectrum, such as the ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003} regions.
However, to obtain the desirable high index of refraction
contrast, layers of high porosity have to be employed, which makes the
resulting structures relatively fragile. In addition, use of high
porosity makes the fabrication of large structures, with a
very large number of layers, unfeasible. For this reason, in this work
we study different strategies to produce multilayered mirrors
with high reflectance omnidirectional band
with relatively small thickness and refractive index contrast.

@@

For the analysis of the propagation of electromagnetic fields through
multilayered systems it is usual to employ the transfer matrix
method \cite{PerezA2004,Pochi2005}. Assuming the system is 1D, with variations
only along the $z$ directions, and that the polarization of light is either
transverse electric (TE) or transverse magnetic (TM), the
transfer matrix $M\left(z_{2},z_{1}\right)$ is
a 2x2 matrix that relates the components of the electric $E_{\| }$
and magnetic  $H_{\|}$ fields parallel to the $xy$ plane
evaluated at $z_2$ to their value at $z_{1}$,
\begin{equation*}
	\left(
	\begin{array}{c}
		E_{\|} \\
		H_{\| }%
	\end{array}%
	\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
	\begin{array}{c}
		E_{\| } \\
		H_{\| }%
	\end{array}%
	\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain and use $M$
\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
for the numerically stable calculation of the reflectance of large
multilayer systems, as
proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the
supplementary information. The
explicit expressions for the optical coefficients are:
\begin{equation}
	r=\sigma \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
		M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
	t=\frac{2\zeta}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $M_{ij}$ are the elements
of the transfer matrix which transfer
the fields from its surface interface with vacuum at $z_0$ towards the
substrate at $z_s$,  $Z_0$ is the surface impedance of vacuum and $Z_s$ is the
surface impedance of the substrate, and we define $r=F_r/F_i$ and $t=F_t/F_i$ in terms
of the reflected and transmitted fields, where we choose the $F$'s as electric
fields for (TE) polarization and magnetic fields
for transverse magnetic polarization (TM). Here, $\sigma=-1$ and
$\zeta= Z_s$ for TE polarization, while
$\sigma=1$ and $\zeta=Z_0$ for TM
polarization.
The reflectance is given by
$R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for
TM polarization. The complex refractive index of the porous
layers were obtained through the Bruggeman's effective medium theory, which
has been reported to adequately reproduce the  optical parameters of PS
\cite{Giusseppe2011,Pap2006,Estrada2018}.

@@

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, $p$-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
\cite{Canham1990,Escorcia2007}. The electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous
hydrofluoric acid (HF) (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
However, as it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte
diffusivity problems \cite{Ariza2011}, the current
densities were chosen as 35 and 305 $\text{mA}/\text{cm}^{2}$,
with corresponding porosities of 51\% and 76\%, respectively.
These porosities were determined through previously obtained calibration
curves using a gravimetric technique \cite{Pap2006}. The
etching rate of PS was obtained by synthetizing single layers under
similar conditions and measuring their thicknesses through Scanning
Electron Microscopy (SEM). Absolute reflectivity measurements were
carried out with a Perkin Elmer Lambda 950 UV/Visible
spectrophotometer with a variable angle universal reflectance
accessory (URA) for different incident angles $\theta _{i}=10^{\circ
}$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $50^{\circ }$ and
$60^{\circ }$ using non-polarized light. The maximum and minimum
values of $\theta _{i}$ were constrained by the angular range of the
URA.

@@

Here we study multilayered structures where the thicknesses for each
pair $j=0\ldots N_p-1$ of layers are tuned to a wavelength $\lambda_j$ which changes
gradually with the depth of the layer, according to
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j}{N_p-1}\right),\label{Dis}
\end{equation}%
\notaL{Quité el -1 en el numerador pues antes pusimos que j empezaba
  en 0}
where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
maximum {\em design} wavelengths respectively, $N_p$ is the number of
periods  in the structure, and $f(\xi)$ is a smooth function that
goes from 0 to 1 as its argument goes from the surface ($\xi=0$) to the
substrate ($\xi=1)$. We only consider increasing functions $f$ due to
the high absorption of PS in the ultraviolet region, which decreases in
the visible and becomes negligible in the near infrared, so, that the first
periods are tuned in the UV-Vis regions. We consider the
following classes of functions:
\begin{equation}
f_{1}\left(\xi \right) =\xi^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
f_{2}\left(\xi \right) =\frac{1}{2}\left(\xi^{\alpha }+\xi^{\beta}\right)
\label{F2}
\end{equation}
and%
\begin{equation}
f_{3}\left(\xi\right) =A\xi^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize in order
to maximize the average reflectance $\braket{R}$ over given spectral
and angular ranges. The class
$f_{1}$ (Eq. (\ref {F1})) with  $\alpha>0$ corresponds to simple
increasing profiles, $f_2$ is the arithmetic mean
of two functions of the type $f_{1}$ with different
powers $\alpha$ and $\beta$, and $f_{3}$ (Eq. (\ref{F3})) is
designed so that the first term dominates near the surface and the
second near the substrate, to allow different behaviors
at the edges of the spectrum.
The parameters
$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize the
reflectance for non-polarized light $\braket{R}$ averaged in the
angular range of $0^\circ$ to $90^\circ$ and either in the
spectral region $\mathcal R_1$ from 350 to
1400 nm or $\mathcal R_2$ from 400 to 3000 nm. For $\mathcal R_1$ we took
$\lambda_{\min}$ as another parameter to be optimized while $\lambda_{\max}$
was fixed at 1400 nm. For $\mathcal R_2$ we fixed both
$\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm.
\notaL{Any reason
	for these choices? They seem arbitrary.} \notaL{Creo que alguna
	explicación  sencilla merece el lector.}
\notaV{Agregue:  }
Approximately $90\%$ of the solar radiation that reaches the
earth's surface is contained in the spectral region
$\mathcal R_1$, and $98\%$ in $\mathcal R_2$ \notaL{¿qué es
  terrestrial solar? terrestrial solar radiation} \cite{Bird1983}. A direct
application of the optimized structures in these regions is solar
reflectors. \notaL{¿Pero por qué en un caso dejasta $\lambda_{\min}$
  fijo y en el otro caso no? Sería bueno que el lector entienda todas
  las decisiones que sean fáciles de explicar}
The
optimized parameters corresponding to the choice $p_l=0.51$ and
$p_h=0.76$ for the low and high porosities
are shown in Table \ref{tab:tableA}.

\begin{table}
  \centering
  \label{tab:tableA}
  \addtolength{\tabcolsep}{-2pt}
    \begin{tabular}{rrrrrrrrrr}
      Class&$\alpha$&$\beta$&A&$\lambda_{min}(nm)$&$N_{p}$&$d(\mu\text{m})$       &ODW(nm)&ODC (nm)&$\braket{R}(\%)$\\
      \hline
      \hline
      $f_{1}$     &0.24    &---      &---     &250&222   &86.1    &300    &1150    &89\\
      $f_{2}$     &0.37    &1.06     &---     &400&102   &35.9    &220    &1110    &88\\
      $\bm{f_{3}}$&\bf 1.23&\bf 0.540&\bf 0.18&\bf 320&\bf 63&\bf 21.6&\bf 250&\bf 1125&\bf 89\\
      \hline
      $\bm{f_{1}}$&\bf 1.20&\bf ---  &\bf --- &\bf ---&\bf 90&\bf 60.4&\bf 2150&\bf 1925&\bf 92\\
      $f_{2}$     &1.08    &1.86     &---  &---  &105   &61.7    &2000    &2000    &89\\
      $f_{3}$     &1.01    &1.95     &0.20  &---  &102   &62.3    &2050    &1975    &90\\
    \end{tabular}
  \caption{Optimized parameters $\alpha$, $\beta$, $A$ and $N_p$ yielding the highest
    reflectance $\braket{R}$ averaged over the spectral ranges
    $\mathcal R_1$ (first block) and $\mathcal R_2$ (second block) and
    the angular range $0-90^\circ$ for the profile classes $f_1$, $f_2$ and
    $f_3$ (Eqs. (\ref{F1}) - (\ref{F3})). We include the thickness $d$
    of the structure and the omnidirectional spectral
    width and center (ODW and ODC).}
\end{table}

The function $f_{3}$ yields after optimization the highest
$\braket{R}$ in the region $\mathcal R_1$ and with the thinnest
structure. Furthermore, this
structure has an omnidirectional width (ODW) of 250 nm
centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b).  Various
photonic structures have been reported with
ODB's \cite{Xu2018,Ahmed2014,Reiner2000} defined as those spectral regions for
which $R>90\%$ for all angles. Here we we adopt the same criterium.
We synthesized a structure designated {\em sample $S_1$} corresponding
to these results. For the region $\mathcal R_2$ the
resulting structures have similar thicknesses and attain similar average reflectance,
though the one with the smallest thickness and the maximum $\braket{R}$
is that obtained from the family $f_{1}$. We
also synthesized the corresponding
structure and designated it {\em sample $S_2$}. The
calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
This structure has a very wide region where $R(\lambda, \theta)>
0.90$, which goes from 850 to 3000 nm, but in a restricted angular range
from $0^\circ$ to $70^\circ$. Thus, it has a
quasi-ODW of 2150 nm centered at 1925 nm.
The functions $f_n$ optimized for the region $\mathcal R_1$ are shown
in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
in Fig. \ref{Fig1}(c). The profiles $f_n$ are qualitatively
similar. For example, for $\mathcal R_1$ the optimal photonic
structures have a small number of periods tuned to the wavelengths where
silicon has a large absorption, i.e.,  the first periods of the
structure.
As withinin $\mathcal R_2$ the absorption of porous silicon is negligible, the optimized $f_n$ are not too
far from a linear profile.
\begin{figure}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=\textwidth]{F1Alternativa.pdf}
  \end{center}
  \caption{Profiles of the functions $f_n(\xi_j)$ \notaL{¿No sería
      mejor rotular el eje horizontal de (a) y (c) como $\xi$ y que
      vaya de 0 a 1? Si no, recuerda que tomamos $j$ va de 0 a $N_p-1$} optimized for
    the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
    $\mathcal R_2$ from 400 to 3000 nm (panel c). Reflectance
    for non-polarized light
    vs. wavelength and angle of incidence of the structure
    optimized for the region $\mathcal R_1$ (panel b) and
    $\mathcal R_2$ (panel d). The dotted lines
    indicate the ODB and the dashed lines
    indicate the quasi-ODB.}
\end{figure}
